Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2019-03-08 Manuscript/manuscript.tex
small corrections to the comments on the works by valentine and hallock

Recent simulations reveal similar trends for the populations at various PS moieties. \cite{valentine18, hallock18}
The results from infrared spectroscopy combined with 
simulations with the CHARMM36 model 
including a correction for overestimated binding of calcium \cite{valentine18}
suggest that POPS interacts mostly through it \ce{COO^-} group. 
In contrast, the combination of NMR experiments 
and MD simulations with the same model but without the correction 
also reveal long-lived interactions of \ce{Ca^{2+}} with \ce{PO4} groups. \cite{hallock18}
The content of POPS in the bilayers in that work is, however, 
much higher above the threshold after which 
\ce{Ca^{2+}} cations induce lipid clustering. \cite{hauser77,kurland79,hauser85,feigenson86,mattai89,roux90,roux91}
At such highly charged membranes,
POPS lipids are found to form even four-membered clusters \cite{hallock18}. 
Our simulations are, however, at different conditions,
in which the clustering of POPS does not happen, 
and PS lipids prefer 1:1 ratio with \ce{Ca^{2+}}
as plotted in Fig.~\ref{fig:cacl_complexes}
showing relative probabilities of \ce{Ca^{2+}} complexes with a certain number of PC or PS lipids. 
Compared to a neutral POPC bilayer
the negatively charged bilayer has its stoichiometry 
shifted towards complexes with three phospholipids and one calcium. 
This is obviously due to the presence of POPS, 
which also contributes to the pre-formed one- and two-membered clusters of POPC. 
Clusters of four or more lipids were not observed in either membrane.

>>>>

Measurements using infrared spectroscopy 
combined with simulations with the CHARMM36 model 
with a correction for overestimated binding of calcium \cite{valentine18}
reveal similar trends for the populations at various PS moieties
suggesting that POPS interacts mostly through its \ce{COO^-} group. 
While this feature agrees nicely with our findings, 
the balance of the interactions of PS moieties with calcium cations may be suboptimal
and the interaction strength underestimated in total \cite{nmrlipids_proj4}.

In contrast, the combination of NMR experiments 
and MD simulations with the same model, CHARMM36, but without the correction for calcium binding
also reveal long-lived interactions of \ce{Ca^{2+}} with \ce{PO4} groups. \cite{hallock18}
Although the ratios of the life times of coordination follow the same trends as in our work,
the lengths of simulation trajectories are insufficient 
to yield converged results in this aspect. \cite{catte16, melcr18, nmrlipids_proj4}
Moreover, the content of POPS in the bilayers in that work is
much higher above the threshold after which 
\ce{Ca^{2+}} cations induce lipid clustering. \cite{hauser77,kurland79,hauser85,feigenson86,mattai89,roux90,roux91}
At such a high content of negatively charged lipids,
PS head groups are found to form even four-membered clusters \cite{hallock18}. 
Our simulations are, however, at different conditions,
in which the clustering of POPS does not happen, 
and PS lipids prefer 1:1 ratio with \ce{Ca^{2+}}
as plotted in Fig.~\ref{fig:cacl_complexes}
showing relative probabilities of \ce{Ca^{2+}} complexes with a certain number of PC or PS lipids. 
Compared to a neutral POPC bilayer
the negatively charged bilayer has its stoichiometry 
shifted towards complexes with three phospholipids and one calcium. 
This is obviously due to the presence of POPS, 
which also contributes to the pre-formed one- and two-membered clusters of POPC. 
Clusters of four or more lipids were not observed in either membrane.
